---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LongituRF

<!-- badges: start -->
[![Documentation](https://img.shields.io/website?url=https%3A%2F%2Fpnavaro.github.io%2FLongituRF%2F)](https://pnavaro.github.io/LongituRF/)

<!-- badges: end -->

The goal of LongituRF implements Random forests for longitudinal
data using stochastic semiparametric miced-model

## Installation

You can install the development version of LongituRF from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("sistm/LongituRF")
```

## Example

Simulate longitudinal data according to the semi-parametric stochastic mixed-effects model

```{r example}
library(LongituRF)
set.seed(123)
data <- DataLongGenerator(n=20) # Generate the data composed by n=20 individuals.
```

Train a SMERF model on the generated data. Should take ~ 50 seconds
The data are generated with a Brownian motion,
so we use the parameter sto="BM" to specify a Brownian motion as stochastic process

```{r merf}
smerf <- MERF(X=data$X,Y=data$Y,Z=data$Z,id=data$id,time=data$time,mtry=2,ntree=500,sto="BM")
```

is the fitted random forest (obtained at the last iteration).

```{r smerf}
smerf$forest 
```

are the predicted random effects for each individual.

```{r random_effects}
smerf$random_effects 
```

are the predicted stochastic processes.

```{r omega}
smerf$omega 
```

```{r plot}
plot(smerf$Vraisemblance) # evolution of the log-likelihood.
```

OOB error at each iteration.

```{r error}
smerf$OOB 
```
